%!TEX encoding = UTF8
%!TEX root =cv-llt.tex
\begin{rubric}{Trainings/Workshops/Certifications}

\subrubric{Trainings}
\entry*[6/24/2025] \textbf{Using the CISA Incident Response Playbook at Your Organization (IR211)} -- Cybersecurity and Infrastructure Security Agency (4 hours) \href{https://github.com/amantaya/curriculum-vitae/blob/master/certifications/IR211_JUN24-2025_CertificateofAttendance.pdf}{\scriptsize\faLink}
\entry*[6/10/2025] \textbf{Understanding Indicators of Compromise Cyber Range Training (IR208)} -- Cybersecurity and Infrastructure Security Agency (4 hours) \href{https://github.com/amantaya/curriculum-vitae/blob/master/certifications/IR208_June10_2025_Course_Completion_Certificate.pdf}{\scriptsize\faLink}
\entry*[6/09/2025] \textbf{Integrating Cyber Threat Intelligence (IR119)} -- Cybersecurity and Infrastructure Security Agency (1 hour). \href{https://github.com/amantaya/curriculum-vitae/blob/master/certifications/IR119_CoC_060925%201.pdf}{\scriptsize\faLink}
\entry*[5/28/2025] \textbf{Defend Against Ransomware Attacks (SS109)} -- Cybersecurity and Infrastructure Security Agency (1 hour). \href{https://github.com/amantaya/curriculum-vitae/blob/master/certifications/SS109_MAY28-2025_CertificateofAttendance.pdf}{\scriptsize\faLink}
\entry*[5/22/2025] \textbf{Introduction to Log Management Cyber Range Training (SS210)} -- Cybersecurity and Infrastructure Security Agency (4 hours). \href{https://github.com/amantaya/curriculum-vitae/blob/master/certifications/SS210_May22_2025_Course_Completion_Certificate.pdf}{\scriptsize\faLink}
\entry*[5/15/2025] \textbf{Incident Response Triage: Mitigation Cyber Range Training (IR218)} -- Cybersecurity and Infrastructure Security Agency (4 hours). \href{https://github.com/amantaya/CV/blob/master/certifications/IR218_COA_051525.pdf}{\scriptsize\faLink}
\entry*[5/12/2025] \textbf{Incident Response Triage: Mitigation (IR118)} -- Cybersecurity and Infrastructure Security Agency (1 hour). \href{https://github.com/amantaya/curriculum-vitae/blob/master/certifications/IR118_CoA_051225.pdf}{\scriptsize\faLink}
\entry*[4/01/2025] \textbf{Introduction to Network Diagraming (SS107)} -- Cybersecurity and Infrastructure Security Agency (1 hour). \href{https://github.com/amantaya/CV/blob/master/certifications/SS107_APR1-2025_CertificateofAttendance.pdf}{\scriptsize\faLink}
\entry*[5/2022] \textbf{CyVerse Advanced Container Camp} -- Dockerfiles, virtual machines (VM), High Performance Computing (HPC), Introduction to Kubernetes (3 days).
\entry*[3/2021] \textbf{CyVerse Container Camp} -- Docker Container basics (1 day).

\subrubric{Workshops}
\entry*[4/2023] \textbf{2023 Research Bazaar} -- \textbf{Instructor.} Data science trainings and discussions (4 days).
\entry*[5/2022] \textbf{2022 Research Bazaar} -- Data science trainings and discussions (4 days).
\entry*[5/2021] \textbf{2021 Research Bazaar} -- Data science trainings and discussions (4 days).
\entry*[2/2020] \textbf{Python Image Processing Workshop} -- Machine learning package “scikit-learn” (2 days).
\entry*[2/2020] \textbf{Data Wrangling with Python Workshop} -- Introduction to shell, git, Python, and Jupyter Notebooks (2 days).

\subrubric{Certifications}
    %
    \entry*[\emph{1/2024}]\textbf{Human Research -- Social and Behavioral Research Investigators} CITI Program. \href{https://github.com/amantaya/CV/blob/286493221d9eb7487b94547a68eb25f92f690e93/certifications/citi-Completion-Certificate_Human-Research_Social-Behavioral-Research-Inverstigators_Basic-Course.pdf}{\scriptsize\faLink}
    %
    \entry*[7/2023] \textbf{SQL Essentials}. LinkedIn Learning. \href{https://github.com/amantaya/CV/blob/12c3c7c23746322f63703f2b4a97c45ef51b4da6/certifications/Certificate-Of-Completion-SQL-Essential-Training.pdf}{\scriptsize\faLink}
    %
    \entry*[7/2021]\textbf{Wildlife Research - Lab Animal Research} CITI Program. \href{https://github.com/amantaya/CV/blob/286493221d9eb7487b94547a68eb25f92f690e93/certifications/citi-Completion-Certificate_Wildlife-Research_Wildlife-Research_Lab-Animal-Research.pdf}{\scriptsize\faLink}
    %
    \entry*[7/2021]\textbf{Working with Cattle in Agricultural Research Settings} CITI Program. \href{https://github.com/amantaya/CV/blob/286493221d9eb7487b94547a68eb25f92f690e93/certifications/citi-Completion-Certificate_Working-with-Cattle-in-Agricultural-Research-Settings_Basic-Course.pdf}{\scriptsize\faLink}
    %
    \entry*[7/2021]\textbf{Working with the IACUC - Investigators, Staff and Students} CITI Program. \href{https://github.com/amantaya/CV/blob/286493221d9eb7487b94547a68eb25f92f690e93/certifications/citi-Completion-Certificate_Working-with-the-IACUC_Working-with-the-IACUC-Investigators-Staff-Students_Basic-Course.pdf}{\scriptsize\faLink}

\end{rubric}
